---
title: "Statistical Inference Course Project Part 1"
output: word_document
---

# Task
In this project you will investigate the exponential distribution in R and compare it with the Central Limit Theorem. The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda. Set lambda = 0.2 for all of the simulations. You will investigate the distribution of averages of 40 exponentials. Note that you will need to do a thousand simulations.

Illustrate via simulation and associated explanatory text the properties of the distribution of the mean of 40 exponentials.  

#1. Show the sample mean and compare it to the theoretical mean of the distribution.

```{r}
set.seed(10)
lambda = 0.2
n = 40

mns = NULL
for (i in 1 : 1000) 
    mns = c(mns, mean(rexp(n, lambda)))
hist(mns,col='blue')
head(mns)
summary(mns)

# Mean
c(mean(mns),1/lambda)

```

#2. Show how variable the sample is (via variance) and compare it to the theoretical variance of the distribution.
```{r}
# Standard deviation
c(sd(mns), 1/lambda/sqrt(n))

# Variance 
c(var(mns), (1/lambda/sqrt(n))^2)
```

#3. Show that the distribution is approximately normal.

```{r}

# Confidence Intervals 
t.test(mns)$conf

```
Actual 95% confidence interval [4.995522, 5.094597]

Note both mean are contained within confidence interval.


#Lets focus on the difference between the distribution of a large collection of random exponentials and the distribution of a large collection of averages of 40 exponentials. 

```{r}
par(mfrow=c(1,2)) 
#The distribution of a large collection of averages of 40 exponentials.
hist(scale(mns),probability=T,main="40 random uniform",ylim=c(0,0.5),xlab='', col='green')
# normal distribution
curve(dnorm(x,0,1),-3,3, col='red',add=T) 
# our distribution 
lines(density(scale(mns)),col='blue') 

#The distribution of a large collection of averages of 1000 exponentials.
n = 1000
mns = NULL
for (i in 1 : 1000) 
    mns = c(mns, mean(rexp(n, lambda)))

hist(scale(mns),probability=T,main="1000 random uniform",ylim=c(0,0.5),xlab='', col='green')
# normal distribution
curve(dnorm(x,0,1),-3,3, col='red',add=T) 
# our distribution 
lines(density(scale(mns)),col='blue') 
head(mns)
summary(mns)

# Mean
c(mean(mns),1/lambda)

# Standard deviation
c(sd(mns), 1/lambda/sqrt(n))

# Variance 
c(var(mns), (1/lambda/sqrt(n))^2)

# Confidence Intervals 
t.test(mns)$conf
```

#Conclusion
This distribution is approximately normal.

The left histogram is more gaussian looking compared to the one the right.

#Appendix

The complete R markdown file for this report can be found at the github repo