---
title: "Statistical Inference Course Project Part 2"
output: word_document
---

# Task
In the second portion of the class, we're going to analyze the ToothGrowth data in the R datasets package.

1.Load the ToothGrowth data and perform some basic exploratory data analyses. 

2.Provide a basic summary of the data.

3.Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (Only use the techniques from class, even if there's other approaches worth considering)

4.State your conclusions and the assumptions needed for your conclusions. 

#The Effect of Vitamin C on Tooth Growth in Guinea Pigs

Description

The response is the length of odontoblasts (teeth) in each of 10 guinea pigs at each of three dose levels of Vitamin C (0.5, 1, and 2 mg) with each of two delivery methods (orange juice or ascorbic acid).

Format

A data frame with 60 observations on 3 variables.

[,1]    len	numeric	Tooth length
[,2]	supp	factor	Supplement type (VC or OJ).
[,3]	dose	numeric	Dose in milligrams.

#1.Load the ToothGrowth data and perform some basic exploratory data analyses.

```{r}
head(ToothGrowth)
str(ToothGrowth)

factor(ToothGrowth$dose)

boxplot(len ~ supp + dose, 
        data=ToothGrowth, 
        col="blue",ylab="Tooth Length", 
        main="Tooth Growth Data in Guinea Pigs")

```

#2.Provide a basic summary of the data.

```{r}
summary(ToothGrowth)
table(ToothGrowth$supp,ToothGrowth$dose)
mean(ToothGrowth$len)
```

#3.Use hypothesis tests to compare tooth growth by supp and dose.

```{r}
g1=ToothGrowth[ToothGrowth$supp=="OJ" & ToothGrowth$dose==0.5,1]
g2=ToothGrowth[ToothGrowth$supp=="VC"& ToothGrowth$dose==0.5,1]
t.test(g1, g2)

g1=ToothGrowth[ToothGrowth$supp=="OJ" & ToothGrowth$dose==1,1]
g2=ToothGrowth[ToothGrowth$supp=="VC"& ToothGrowth$dose==1,1]
t.test(g1, g2)

g1=ToothGrowth[ToothGrowth$supp=="OJ" & ToothGrowth$dose==2,1]
g2=ToothGrowth[ToothGrowth$supp=="VC"& ToothGrowth$dose==2,1]
t.test(g1, g2)

```


#4.Conclusion
When the dosage is 0.5 and 1 mg, OJ dosage type result in larger tooth growth than VC dosage type. 

When the dosage is 2 mg, there isn't statistical difference in tooth growth between VC and OL types.

#5.Appendix

The complete R markdown file for this report can be found at the github repo: https://github.com/tsopronyuk/Statistical-Inference